%-------------------------
% Resume in Latex
% Author : Stephen Wnag
% Based off of: https://github.com/zhongqi1112/Hulk/tree/master/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------


%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%-----------HEADING-----------
\begin{center}
    \textbf{\large \scshape Stephen Z. Wang} \\ \vspace{1pt}
    \href{mailto:stephen.wang@gatech.edu}{\underline{stephen.wang@gatech.edu}} $|$ 
    % \href{https://linkedin.com/in/stephenzwang}{\underline{linkedin.com/in/stephenzwang}} $|$
    \small (626)236-8684 $|$
    \href{http://stephenwang.me}{\underline{http://stephenwang.me}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Jan. 2019 -- May 2021}
      {Master of Science, Computer Science, Specialization in Machine Learning}{}
    \resumeSubheading
      {University of California, Los Angeles}{Sep. 2014 -- June 2017}
      {Bachelor of Science, Mathematics of Computation}{}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript, C/C++, HTML/CSS, SQL, Lisp, Scala, Bash, Matlab} \\
     \textbf{Frameworks}{: TensorFlow, PyTorch, ScikitLearn, Caffe, Keras, SpringBoot, Maven, Vue.js, Node.js} \\
     \textbf{Developer Tools}{: Git, Docker, Jenkins, SonarQube, Kubernetes, Linux}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Northrop Grumman Corporation, Defense Systems}{Aug. 2017 -- Present}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Designed, developed, integrated, and tested software}
        \resumeItem{Determined user needs and analyzed system capabilities to resolve problems on program intent}
        \resumeItem{Architected, designed and developed advanced system and realize the concept into prototype or production system}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
    % \resumeSubSubheading
    % {Software Engineer}{Oct 2014 - Sep 2016}
    % \resumeItemListStart
    %     \resumeItem{Apache Beam}
    %      {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
    % \resumeItemListEnd
    % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {United States Navy}{Oct. 2014 -- Present}
      {Machinist’s Mate}{}
      \resumeItemListStart
        \resumeItem{Supported the 25th Rim of the Pacific Exercise, the world's largest international maritime warfare exercise}
        \resumeItem{Attended Pacific Blitz Exercise, scenario-driven joint Marine Corps replicating a realistic maritime threat}
        \resumeItem{Operated, maintained, and repaired propulsion machinery, auxiliary equipment in Coronado, San Diego}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Common Control System Processing, Exploitation, and Dissemination}}{Oct. 2019 -- Present}
          \resumeItemListStart
            \resumeItem{Built a single control station that can use PED services to obtain sensor imagery/FMV files from Unmanned Systems across Aviation, Surface, Sub-Surface, and Ground domains worked with Raytheon for PMA-281 under Naval Air System Command (NAVAIR)}
            \resumeItem{Implemented DevOps services in C++ and deployed on Docker with integration testing of Jenkins, SonarQube, GCov and etc. on Linux OS in the agile development scrum team}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Real-time data for Coronavirus (COVID-19)}}{Apr. 2020 -- May 2020}
          \resumeItemListStart
            \resumeItem{Real-time data of COVID-19 cases in the U.S. simply and intuitive visualization}
            \resumeItem{Implement and designed a website in VueJS and visualize the map with real-time data in D3.js}
            \resumeItem{Fetch, clean, and deal with data from a real-time database}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Cost of Buying/Renting Algorithm}}{Oct. 2019 -- Dec. 2019}
          \resumeItemListStart
            \resumeItem{The Cost of Buying/Renting Algorithm (COBRA) to help home-seekers process the overwhelming amount of data points involved in buying or renting a home to make an optimal decision}
            \resumeItem{Designed and implemented front-end web client application on Pyramid framework with D3.js in Python}
          \resumeItemListEnd
         
      \resumeProjectHeading
          {\textbf{Electronic Warfare Battle Management}}{Apr. 2018 -- Oct. 2020}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application using a REST API and WebSocket with Vue.js and Node.js}
            \resumeItem{Designed and built spring boot application using Maven in Java for CRUD type operations of data}
            \resumeItem{Implemented critical abstraction layer (CAL) using ActiveMQ and RabbitMQ  to implement Java Messaging Service (JMS) to publish and subscribe RTI DDS server}
            \resumeItem{Deployed front-end and back-end applications to Tomcat server on different OS VMs}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
